Marlowe: implementing and analysing financial contracts\thanks{Supported by IOHK.}

### 2019-11-28 papers/marlowe2019/paper.tex
Add Makefile and change permissions
Mis-spelled title

\begin{document}
%
\title{Marlowe: implmenting and analysing financial contracts\thanks{Supported by IOHK.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{
Pablo Lamela Seijas\inst{1} \and
Alex Nemish\inst{1} \and
David Smith\inst{1} \and
Simon Thompson\inst{1,2}\orcidID{0000-0002-2350-301X}}
%
\authorrunning{P. L. Seijas, A. Nemish, et al.}

@@

[There’s some stuff on this in the tutorial.]

@@

\begin{figure}
\includegraphics[width=\textwidth]{fig1.eps}
\caption{A figure caption is always placed below the illustration.
Please note that short captions are centered, while long ones are
justified by the macro package automatically.} \label{fig1}
\end{figure}

>>>>

\begin{document}
%
\title{Marlowe: implementing and analysing financial contracts\thanks{Supported by IOHK.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{
Pablo Lamela Seijas\inst{1} \and
Alex Nemish\inst{1} \and
David Smith\inst{1} \and
Simon Thompson\inst{1,2}\orcidID{0000-0002-2350-301X}}
%
\authorrunning{P. L. Seijas, A. Nemish, et al.}

@@

[There's some stuff on this in the tutorial.]

@@

%\begin{figure}
%\includegraphics[width=\textwidth]{fig1.eps}
%\caption{A figure caption is always placed below the illustration.
%Please note that short captions are centered, while long ones are
%justified by the macro package automatically.} \label{fig1}
%\end{figure}
